\Title

### 2020-12-09 manuscript/manuscript.tex
Make a tiny change to trigger the actions build

% Configure header and hypersetup
% ===============================
\pagestyle{fancy}
\fancyhf{}
\lhead{
    \fontsize{9pt}{12pt}\selectfont
    \Author{}, 2019. \DOI{}
}
\rhead{\fontsize{9pt}{12pt}\selectfont \thepage}
\renewcommand{\headrulewidth}{0pt}
\hypersetup{
    allcolors=blue,
    pdftitle={\Title},
    pdfauthor={\Author},
}

@@

\section{Performance of gradient boosted equivalent sources}

Our second goal is to assess the accuracy of the predictions achieved by the
gradient boosting algorithm while registering its performance by comparison
with the non-boosted equivalent sources.

\subsection{Window size}

One factor that plays an important role on the gradient boosted equivalent
layers is the size of the overlapping windows used to create each set of
equivalent sources.
Smaller windows will reduce the amount of computer memory needed to fit the
source coefficients: smaller windows will reduce the size of Jacobian matrices
$\tilde{\mathbf{A}_k}$.
Nevertheless, the usage of smaller windows may produce less accurate
predictions: the equivalent sources cannot achieve the global minimum of the
misfit $\varphi(\mathbf{c})$ of equation~\ref{eq:misfit-unscaled}.
Moreover, the size of the overlapping windows might also impact on the
computation time needed to fit the source coefficients: smaller windows will
generate simpler least-square problems which are easier to solve, but they will
also create more iterations.

We want to assess how the size of the overlapping windows impacts both the
accuracy of the predictions and the computation time needed to fit the source
coefficients in comparison with the performance of the non-boosted equivalent
sources.

We applied the gradient boosted equivalent sources to interpolate the synthetic
airborne survey on the same points of the target grid.
We selected several window sizes to assess how accuracy and performance depend
on that variable.
For each window size we gridded the synthetic data with different sets of
parameters. Then we compared each prediction to the target grid in order to get
the best prediction for each window size.
On every interpolation, block-averaged sources with relative depth are used
with a spacing of
\SI{\BestAirborneBlockAveragedSourcesConstantDepthSpacing}{\meter}, and an
overlap of 50\% between adjacent windows.

Using the best set of parameters for each window size, we registered the
achieved RMS against the values of the target grid and the time needed to fit
the sources coefficients.

Compare RMS with the one achieved by the best prediction carried out by the
non-boosted equivalent sources with block-averaged sources (see
Table~\ref{tab:parameters-airborne-survey}).
Calculated the fitting time relative to the time needed by non-boosted
equivalent sources.

\subsection{Overlapping}

Another factor that plays an important role on the accuracy of the predictions
and impacts the computation time needed to fit the source coefficients is the
amount of overlap between adjacent windows.
The previous choice of 50\% showed to be sufficiently good to achieve
acceptable accuracy, although a deeper study should be carried out to assess
how the amount of overlap impacts both accuracy and fitting time.

We interpolated the synthetic airborne survey using the gradient boosted
equivalent sources on the same points of the target grid.
The interpolations were carried out using different amount of overlap, from
0\% to 0.95\% with a step size of 0.05\%.
For each overlap, we gridded the synthetic data with different sets of
parameters, fixing the window size to INSERT-WINDOW-SIZE and using
block-averaged sources with relative depth and a spacing of
\SI{\BestAirborneBlockAveragedSourcesConstantDepthSpacing}{\meter}.
We registered the RMS achieved by the best prediction for each overlap and the
computation time needed to fit the source coefficients.

\section{Gridding Australia gravity data}

>>>>

% Configure header and hypersetup
% ===============================
\pagestyle{fancy}
\fancyhf{}
\lhead{
    \fontsize{9pt}{12pt}\selectfont
    \Author{}, 2020. \DOI{}
}
\rhead{\fontsize{9pt}{12pt}\selectfont \thepage}
\renewcommand{\headrulewidth}{0pt}
\hypersetup{
    allcolors=blue,
    pdftitle={\Title},
    pdfauthor={\Author},
}

@@
